\renewcommand{\abstractname}{摘要}  % 将Abstract改为摘要
\begin{center}
   \large{\textbf{摘要}}
\end{center}
\begin{adjustwidth}{0cm}{0cm}
   \hspace{2em}为了实现对无人机的自稳定控制, 首先对四旋翼无人机进行了动力学建模, 提出了一
   种改变学习率的 BP 神经网络算法与 PID 控制相结合的姿态控制方法, 并在相同环境下与常规 PID
   控制器进行了仿真试验对比. 仿真试验结果表明: 基于改进型 BP 神经网络的 PID 控制器能够有效
   地实现无人机的自稳定控制, 相比于常规 PID 控制器, 基于改进型 BP 神经网络的 PID 控制器具有
   响应速度快、 超调量低、 鲁棒性强等优点.比例积分微分控制，简称PID控制，是最早发展起来的控制策略之一，由于其算法简单、鲁棒性好和可靠性高，被广泛应用于工业过程控制，至今仍有90\%左右的控制回路具有PID结构。
   简单的说，根据给定值和实际输出值构成控制偏差，将偏差按比例、积分和微分通过线性组合构成控制量，对被控对象进行控制。常规PID控制器作为一种线性控制器。
   
   \begin{flushleft}
   \par\textbf{关键字: } 无人机; BP神经网络; PID控制 %“\par在段首，表示另起一行，“\textbf{}”,花括号内的内容加粗显示
   \end{flushleft}
\end{adjustwidth}
\thispagestyle{empty} % 设置当前页 页版式
\clearpage % 分页

\begin{center}
   \large{\textbf{Abstract}}
\end{center}
% adjustwidth \usepackage{changepage}
\begin{adjustwidth}{0cm}{0cm}
   \hspace{1.5em}In order to realize the self-stability control of the UAV, firstly, the four-rotor UAV was dynamically modeled, and an attitude control method combining the BP neural network algorithm with PID control and the PID control was proposed. Compared with conventional PID controller in the environment, the simulation test results show that the PID controller based on the improved BP neural network can effectively achieve the self-stability control of the UAV, compared with the conventional PID controller, based on the improvement The PID controller of the BP neural network has the advantages of fast response, low overshoot, and strong robustness. Proportional integral differential control, or PID control for short, is one of the earliest developed control strategies. Due to its simple algorithm and robust It has good stickiness and high reliability, and is widely used in industrial process control. So far, about 90\% of the control loops have PID structure.\par
   \noindent\hspace{1.5em}Simply put, according to the given value and the actual output value to form a control deviation, the deviation is proportionally, integrally and differentially combined into a control quantity by a linear combination, and the controlled object is controlled. The conventional PID controller serves as a linear controller. \par
   % \noindent 首行缩进
\end{adjustwidth}
% 关键词 % \providecommand{\keywords}[1]{\textbf{\textit{Index terms---}} #1}
\begin{keywords}
   \noindent UAV, BP neural network, PID control          
\end{keywords}
\thispagestyle{empty} % 设置当前页 页版式